Fréchet Distance

### 2022-12-01 docs/paper.tex
wip: Fréchet distance free space figures

% TODO: Why allow it? Better algorithms?
\subsection{Weak Fréchet distance}
The \textit{weak Fréchet distance} (non-monotone Fréchet distance) slightly modifies the continuous version by allowing 
going backwards.

% Discrete Fréchet distance
\subsection{Discrete Fréchet distance}
The \textit{discrete Fréchet distance} is specifically tied to 
polygonal curves (\autoref{def_polygonal_curve}) 
because it requires a finite number of vertices 
and forbids walking or staying in between them.
The dog walking analogy can be adapted by replacing both the man and the dog by two frogs,
which are only allowed to jump from their current vertex to their next 
vertex in forward direction \cite{bringmann_why_2014}.
While it is allowed for both frogs to jump simultaneously,
it is not allowed to skip vertices while jumping. 
We ensure this behavior by defining a coupling between the curves in \autoref{def_point_coupling}.

@@

@@

\subsection{Original algorithm for the continuous Fréchet distance}
\label{sec_original_algorithm}
The original algorithm to compute the continuous Fréchet distance (\autoref{def_frechet_distance})
is based on the idea of solving a simpler decision problem and then doing a parameter search to find the exact value of $\delta_{F}$.
The decision problem is to decide whether two polygonal curves $P$ and $Q$ have a 
Fréchet distance $\delta_{F}(P,Q) \leq \varepsilon$ for some fixed $\varepsilon \geq 0$.

@@

% Free Space Diagram
\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
      }
      \caption{Line segments $P$ and $Q$}
      \label{fig_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-bad-example.pdf}
      }
      \caption{Free space diagram}
      \label{fig_free_space_diagram_example}
  \end{subfigure}
  \caption[Free space diagram example]{
    The free space diagram \autoref{fig_free_space_lines_example} 
    for line segments $P$ and $Q$ and distance $\varepsilon$
    from \autoref{fig_free_space_lines_example} using euclidean distance.}
  \label{fig_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
      }
      \caption{Polygonal curves $P$ and $Q$}
      \label{fig_complex_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-bad-example.pdf}
      }
      \caption{Free space diagram}
      \label{fig_complex_free_space_diagram_example}
  \end{subfigure}
  \caption[Complex free space diagram example]{
    The free space diagram \autoref{fig_complex_free_space_diagram_example} 
    for polygonal curves $P$ and $Q$ and distance $\varepsilon$ 
    from \autoref{fig_complex_free_space_lines_example} using euclidean distance.}
  \label{fig_complex_free_space}
\end{figure}

>>>>

% TODO: Why allow it? Better algorithms?
\subsection{Weak Fréchet Distance}
The \textit{weak Fréchet distance} (non-monotone Fréchet distance) slightly modifies the continuous version by allowing 
going backwards.

% Discrete Fréchet distance
\subsection{Discrete Fréchet Distance}
The \textit{discrete Fréchet distance} is specifically tied to 
polygonal curves (\autoref{def_polygonal_curve}) 
because it requires a finite number of vertices 
and forbids walking or staying in between them.
The dog walking analogy can be adapted by replacing both the man and the dog by two frogs,
which are only allowed to jump from their current vertex to their next 
vertex in forward direction \cite{bringmann_why_2014}.
While it is allowed for both frogs to jump simultaneously,
it is not allowed to skip vertices while jumping. 
We ensure this behavior by defining a coupling between the curves in \autoref{def_point_coupling}.

@@

\subsection{Fréchet Distance for Uncertain Curves}

@@

\subsection{Original Algorithm for the Continuous Fréchet Distance}
\label{sec_original_algorithm}
The original algorithm to compute the continuous Fréchet distance (\autoref{def_frechet_distance})
is based on the idea of solving a simpler decision problem and then doing a parameter search to find the exact value of $\delta_{F}$.
The decision problem is to decide whether two polygonal curves $P$ and $Q$ have a 
Fréchet distance $\delta_{F}(P,Q) \leq \varepsilon$ for some fixed $\varepsilon \geq 0$.

@@

% Free Space Diagram
\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/line_segments.pdf}
      }
      \caption{Line segments $P$ and $Q$}
      \label{fig_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/free_space_single_cell.pdf}
      }
      \caption{Free space diagram}
      \label{fig_free_space_diagram_example}
  \end{subfigure}
  \caption[Free space diagram example]{
    The free space diagram \autoref{fig_free_space_diagram_example} 
    for line segments $P$ and $Q$ and distance $\varepsilon$
    from \autoref{fig_free_space_lines_example} using euclidean distance.}
  \label{fig_free_space}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  % TODO: update figure graphics
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/polygonal_curves.pdf}
      }
      \caption{Polygonal curves $P$ and $Q$}
      \label{fig_complex_free_space_lines_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/frechet_distance/free_space_polygonal_curves.pdf}
      }
      \caption{Free space diagram}
      \label{fig_complex_free_space_diagram_example}
  \end{subfigure}
  \caption[Complex free space diagram example]{
    The free space diagram \autoref{fig_complex_free_space_diagram_example} 
    for polygonal curves $P$ and $Q$ from \autoref{fig_complex_free_space_lines_example} 
    and distance $\varepsilon = 0.73$ using euclidean distance.}
  \label{fig_complex_free_space}
\end{figure}
